Perceptions of Information Disclosure Risks for Wearable Devices

### 2016-01-29 USEC2016-camera-ready/camera-ready.tex
fixing ugly formatting from template transition

To reduce fatigue, we gave our participants a randomly selected subset of wearables scenarios. The average survey completion time was 11.5 minutes, which includes four questions that we omitted from this paper due to lack of participants' familiarity with specific devices and a misguided attempt to directly compare smartphones and wearables. See Appendix \ref{sec:noquestions} for details.

\subsubsection{Comprehension Questions}
The beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks. Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we framed our scenarios on a fictitious wearable. We highlighted the capabilities of this device and described use cases:

@@

To guarantee that participants had understood its capabilities, we asked two multiple-choice comprehension questions and filtered out responses from participants who did not answer both questions correctly.

\subsubsection{Wearable Scenarios}
We presented scenarios involving data captured by the Cubetastic3000 and asked participants to rate how upset they would be if a particular type of data (e.g., how much you exercise) was shared without permission with a particular recipient (e.g., work contacts). The purpose for using this question format was to determine how upset participants would be if data were inappropriately shared, and the extent to which their reactions were based on the data type and recipient. Responses were reported on a 5-point Likert scale (from ``indifferent'' to ``very upset''). Figure \ref{fig:prompt} shows an example.  Specifically, questions were of the form:

@@

The participants were presented with a blank box to write in, with no particular suggestion on what to talk about, and with no character limit to their open-ended responses. Table \ref{openresponses} shows common user concerns related to wearable devices. Appendix \ref{sec:coding} details the responses categorized in each coding label. Note that participants were especially concerned with privacy and security, however, we do realize that we asked this open-ended question after we had exposed our participants to a variety of privacy-related scenarios, which may have heightened their awareness of the possible privacy and security risks.

@@

\noindent
\textit{P1256: ``They can be hacked and then your security will be compromised.''}
\end{quotation}

Other significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from EMF waves (Health), and safety hazards from wearing the device, such as distractions that cause car accidents (Safety).

@@

Interestingly, a modest amount of participants were also concerned with resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact).

\begin{quotation}
\noindent
\textit{P1425: I think the biggest risk is how they may effect society as a whole... a wearable technology that's always on and available may push things even further to the point where people spend less time actually interacting with loved ones, and applying their own critical thinking in certain situations, instead always relying on their devices.}
\end{quotation}

>>>>

To reduce fatigue, we gave our participants a randomly selected subset of wearables scenarios. The average survey completion time was 11.5 minutes, which includes four questions that we omitted from this paper due to lack of participants' familiarity with specific devices and a misguided attempt to directly compare smartphones and wearables. See Appendix \ref{sec:noquestions} for details.\\

\noindent {\bfseries Comprehension Questions}
The beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks. Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we framed our scenarios on a fictitious wearable. We highlighted the capabilities of this device and described use cases:

@@

To guarantee that participants had understood its capabilities, we asked two multiple-choice comprehension questions and filtered out responses from participants who did not answer both questions correctly.\\

\noindent {\bfseries Wearable Scenarios}
We presented scenarios involving data captured by the Cubetastic3000 and asked participants to rate how upset they would be if a particular type of data (e.g., how much you exercise) was shared without permission with a particular recipient (e.g., work contacts). The purpose for using this question format was to determine how upset participants would be if data were inappropriately shared, and the extent to which their reactions were based on the data type and recipient. Responses were reported on a 5-point Likert scale (from ``indifferent'' to ``very upset''). Figure \ref{fig:prompt} shows an example.  Specifically, questions were of the form:

@@

The participants were presented with a blank box to write in, with no particular suggestion on what to talk about, and with no character limit to their open-ended responses. Table \ref{openresponses} shows common user concerns related to wearable devices. Appendix \ref{sec:coding} details the responses categorized in each coding label. Note that participants were especially concerned with privacy and security, however, we do realize that we asked this open-ended question after we had exposed our participants to a variety of privacy-related scenarios, which may have heightened their awareness of the possible privacy and security risks. \\

@@

\noindent
\textit{P1256: ``They can be hacked and then your security will be compromised.''}\\
\end{quotation}

Other significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from EMF waves (Health), and safety hazards from wearing the device, such as distractions that cause car accidents (Safety).\\

@@

Interestingly, a modest amount of participants were also concerned with resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact). \\

\begin{quotation}
\noindent
\textit{P1425: I think the biggest risk is how they may effect society as a whole... a wearable technology that's always on and available may push things even further to the point where people spend less time actually interacting with loved ones, and applying their own critical thinking in certain situations, instead always relying on their devices.}\\
\end{quotation}
